The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
temporal scale

We altered the temporal scale of multilayer networks using a moving time-window
approach to define seasons and

1. time window length

Varying length of time window (used to define seasons). Starting with a window
of day 1-40 and using a moving window to go to day 1-100. Fixed start julian day
for winter is day 1 and for summer is 215. Network layers for winter and summer
are calculated for each window length.

1. time window position
Varying position of time window (used to define seasons). Fixed length at 48
Window positions starting at 1, to + 48 So 1-48 is first iteration for winter
and 48-96 is second iteration for "winter". Same for summer, starting at 215.
Network layers for each season are constructed.

**Observational scale** <!--(temporary header)-->: Studies of social network analysis
vary in the number and frequency of observations as well as the data collection
technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
2019).

Randomly select max number of observations - timegroups - <!-- (right now 750)-->. For
each iteration, include n observations for each season for all individuals.
Subsequent iterations include nstep more <!--(right now 25)-->, along with previously
included to remove stochasticity. Parallels with observation data.

@@

(ref:socres) varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:winlen) varying scale in time window length. For each time window length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:nobs) varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

@@

(ref:winpos) varying scale in time window position. For each time window position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.

>>>>

We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (1 January)
and summer (3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale, we investigated the influence of the number of observations on
resulting multilayer networks. We randomly selected 500 timesteps and
iteratively included 25 additional observations, regenerating the multilayer
network and calculating associations of individuals. Subsequent iterations
included the previous set of observations to mimic observational data.

@@

(ref:socres) Varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest. This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 **[JWT: Does this have units??]** at approximately a 50m **??** social threshold before decreasing between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections. **[JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI. I would talk about it more about strong/weak connections. Networks can be sparse (few connections), but still have high strength if the ties have higher values]**

@@

(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window **[JWT: previously this was describing fig. 3. I don't know if what I wrote best encapsulates what connnective redundancy does here. Length of time window seems to make connective redundancy highly variable as it changes.]**. C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer. D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. **[see if you agree with my changes. B-D were based off fig. 3 and not relevant to this figure]**

@@

(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. *There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**. B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.

@@

(ref:winpos) Varying scale in time window position. For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows. **[JWT: previously describing window length, not position. Check that you're ok with my changes]** B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
